### 2024-02-13 documentation/thesis/thesis_document.tex
.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field MRI is the improved imaging of
soft tissues, especially when examining joints and muscles. It also
offers more cost-effective alternatives to high-field MRI systems
\cite{Hori2021-pt}.

Contemporary most MRI machines employ high-field superconducting magnets
cooled cryogenically, delivering exceptional image resolution. However,
the associated costs, space requirements, and safety considerations can
be substantial. In contrast, permanent magnets present an economical and
space-efficient alternative. Nevertheless, they generate lower magnetic
field strengths, impacting the signal-to-noise ratio (SNR) and resulting
in lower image resolution within clinically viable scan times.
\cite{Arnold2023-cn}

In response to these challenges, recent endeavors in both academia and
industry aim to leverage the benefits of lower field strength---such as
reduced costs, a smaller device footprint, and diminished safety
concerns---while addressing the inherent drawbacks that compromise image
quality (refer to Table 1). The optimization of low-field approaches is
becoming increasingly prevalent, tailored to specific clinical inquiries
and contexts.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of 0T to 3T with a resolution of
0.1mT. It offers an RS232 interface with a documented protocol
\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.

@@

@@

@@

@@

The sensor platform used here is a ready-built
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
platform, which has been equipped with the sensors to be measured one
after the other.

>>>>

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri} is the improved
imaging of soft tissues, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}.

Contemporary most \gls{mri} machines employ high-field superconducting
magnets cooled cryogenically, delivering exceptional image resolution.
However, the associated costs, space requirements, and safety
considerations can be substantial. In contrast, permanent magnets
present an economical and space-efficient alternative. Nevertheless,
they generate lower magnetic field strengths, impacting the \gls{snr}
and resulting in lower image resolution within clinically viable scan
times. \cite{Arnold2023-cn}

In response to these challenges, recent endeavors in both academia and
industry aim to leverage the benefits of lower field strength---such as
reduced costs, a smaller device footprint, and diminished safety
concerns---while addressing the inherent drawbacks that compromise image
quality. The optimization of low-field approaches is becoming
increasingly prevalent, tailored to specific clinical inquiries and
contexts.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of 0T to 3T with a resolution of
0.1mT. It offers an RS232 interface with a documented protocol for
connection to a \gls{pc}.

@@

\begin{itemize}
\tightlist
\item
  TODO
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
\caption{Sensor evaluation plattform with TLV493D and MMC5603 sensors
placed with thermal conductive glue on an aluminium baseplate
\label{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}}
\end{figure}

@@

The sensor platform used here is an adapted version of the
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} sensor
platform. The sensors to be measured were fixed together on an aluminium
plate with thermally conductive adhesive. This compensates for thermal
differences.

This is crucial for the subsequent temperature deviation tests in order
to obtain comparable measurement results. The graphic
\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
shows this basic setup, the Raspberry Pi Pico shown here was used as the
readout hardware, on which the Unified Sensor Firmware version
\passthrough{\lstinline!1.0.2!} is running.

A separate \passthrough{\lstinline!KA30005D!} laboratory power supply is
used as the power supply for the sensors. An Raspberry Pi 4 is used as
the host computer, which is connected to the sensors via a
\passthrough{\lstinline!Hailege ADUM3160!} \gls{usb} isolator and is
placed outside the temperature chamber. \passthrough{\lstinline!MRPCli!}
\ref{command-line-interface} version \passthrough{\lstinline!1.5.0!} was
used to control and record the measurement series, with the functions of
the \passthrough{\lstinline!MRPDataVisualisation!}
\ref{mrpvisualisation} and \passthrough{\lstinline!MRPAnalysis!}
\ref{mrpanalysis} packages from the library
\ref{software-readout-framework} being used for subsequent evaluation.
The recorded measurement series are automatically analysed using the
\passthrough{\lstinline!Programmable-  Data Pprocessing Pipeline!}
\ref{programmable-data-processing-pipeline} and the results are
visualised.

@@
